\Title

### 2021-01-26 manuscript/manuscript.tex
Finish review of the window overlap section

\subsubsection{Amount of overlap}

Another factor that plays an important role on the performance of the gradient
boosted equivalent sources is the amount of overlap between adjacent windows.
The previous choice of 50\% showed to be sufficiently good to achieve
acceptable accuracy, although a deeper study should be carried out to assess
how the amount of overlap impacts both accuracy and fitting time.

We interpolated the synthetic airborne survey using the gradient boosted
equivalent sources on the same points of the target grid.
The interpolations were carried out using different amount of overlap, from
0\% to 0.95\% with a step size of 0.05\%.
For each overlap we gridded the synthetic data using block-averaged sources
with a spacing of
\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter},
a relative depth of
\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter},
a window size of \BoostOverlappingWindowSize, and with different
values of damping.
Then we compared the resulting interpolations with the target grid in order to
get the best prediction for each overlap and the damping value used to
obtain it.

Using the best set of parameters for each overlap, we registered the achieved
RMS against the values of the target grid and the time needed to fit the
sources coefficients.
The RMS was obtained as the mean RMS achieved by using different random seeds
as we did on~\ref{sec:window_size}.

We have also computed the fitting time ratio for each overlap, in a similar way
we did for the window sizes (see Fig.~\ref{fig:gradient-boosted-comparison}d).

From the results obtained we can conclude that a lower values of overlap
generates less accurate results, while a higher overlap increases the
computational time required for fitting the source coefficients due to the
significant increment of the number of overlapping windows.

We found that overlaps less than 40\% produce very inaccurate predictions in
comparison with the non-boosted equivalent sources, while values larger that
80\% produce predictions with almost the same level of accuracy as the latter.
Nevertheless, overlap values larger that 70\% takes significantly more
computational time to fit the source coefficients.

THE FOLLOWING PARAGRAPH SHOULD BE IN DISCUSSION?

@@

>>>>

\subsubsection{Window overlap}

The amount of overlap between adjacent windows plays an important role in the
performance of the gradient-boosted equivalent sources.
It controls the number of iterations and how often a particular source is used
in the least-squares fitting process.
While the experiments in the previous section showed that 50\% overlap was
sufficient to achieve acceptable interpolation accuracy, we separately studied
the impacts of the amount of window overlap on both accuracy and computation
time.

We performed a similar experiment to one in section~\ref{sec:window_size} but
this time kept the window size fixed to \BoostOverlappingWindowSize{} and
varied the amount of overlap from 0\% to 95\% with a step size of 5\%.
All other experimental procedures remained unchanged.
Figs.~\ref{fig:gradient-boosted-comparison}b and
\ref{fig:gradient-boosted-comparison}d show the RMS error and computation time
required for estimating the source coefficients, respectively, as a function of
the window overlap.

Our results show what the interpolation RMS error decreases with the amount of
overlap, reaching the same accuracy as the regular equivalent sources at
approximately 90\% overlap.
On the other hand, the computation time increases with the amount of overlap,
becoming larger than that of the regular equivalent sources for overlaps
greater than 70\%.
This is expected since increasing the overlap adds iterations to the gradient
boosting algorithm without decreasing the individual least-squares problem
sizes to compensate.

@@

Overlap:
